---
title: "Untitled"
author: "Bobby Fatemi"
date: "September 15, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intuitive Surgical Data Science

The R package ISDS provides the functionality to execute a PSM analysis across cohorts of patient modalities. Additionally, once cohorts of patients are matched across modalities, this package runs basic statistics to analyze the difference in various outcomes across groups.

There are a number of functions available, however, the entire workflow can be run in 1 line of R code. This vignette aims to guide the user through the available analysis functions. 

Current on-going efforts have integrated these analytics into Intuitive Surgical's data pipelines; however, these functionalities can be used by any employee at ISI that has been granted access. 

*Note*: If you would like access to utilize these functions, please reach out to the package author: 

Bobby Fatemi
Data Scientist
Bobby.Fatemi@intusurg.com


## Install Package

```{r install, eval=FALSE}

library(devtools)
install_github("bfatemi/isds")

```

## Run Entire PSM Workflow

As mentioned, if the user desires to execute the entire the workflow without needing fine-grain control, this can be accomplished in 1 line:

```{r runPSM, eval=TRUE}

library(isds)
resultDT <- runPSM()

```



