---
title: "Install ISDS"
author: "Bobby Fatemi"
date: "July 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Install Packages

```{r install, eval=FALSE}
install.packages("curl")     # if not already installed
install.packages("devtools") # if not already installed

source("https://install-github.me/hadley/rlang")
source("https://install-github.me/gaborcsardi/secret")
source("https://install-github.me/bfatemi/isds")

```

### Set Environment Var

The system variable `USER_KEY` tells the package where the private key is located, which is associated with a public key that was used to encrypt the connection parameters to our internal db.

This is how you set environment vars in the R session:

```{r setenv, eval = FALSE}
Sys.setenv(USER_KEY = "path/to/privatekey")
```

You can set this variable in the R environment, but it must be set every time a new session is created. Therefore, I would recommend setting this variable at the system level

### Load Library

Load our ISI package and run as follows:

```{r loadrun}
library(isds)
result <- runPSM(hosp_id = 10112)
```


